User-level Grid Monitoring with Inca 2

### 2007-02-27 papers/hpdc-gmw-2007/paper.tex
fixed two user-level grid monitoring bullets that were bugging me
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6597 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

\item User-level tests and performance measurements should be written and
maintained within an iterative refinement process.  An iterative process is
required because Grids are dynamic and software environments change over time as
packages are upgraded.  It is also difficult to write and deploy a test
correctly the first time because of portability issues and incomplete user
documentation.  It often requires multiple iterations to determine whether a
detected failure stems from a faulty test, user document, or Grid resource.

\item In order to determine overall Grid health, monitoring must be flexible
enough to include many types of user-level tests and performance measurements.
Typically, tests for each command listed in the user documentation and/or for
each software component of the Grid infrastructure are required.

>>>>

\item User-level tests and performance measurements should be easy to update
and maintain as they are often revised due to Grid infrastructure upgrades.
It is also difficult to write and deploy a test correctly the first time
because of portability issues and incomplete user documentation.  Multiple
iterations are usually required to determine whether a detected failure stems
from a faulty test, user documentation, or Grid resource.

\item Many types of user-level tests and benchmarks can be used to monitor 
Grid infrastructure.  Testing documented user commands and individual Grid
software components provides a representative indication of Grid status.
